quollr: An R Package for Visualizing \(2-\text{D}\) Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-08 paper-quollr.tex
Got the trimesh with small edges

#> # A tibble: 324 x 8

@@

#> # i 314 more rows

@@

trimesh <- gen_edges(tri_object = tr_object)
trimesh
\end{verbatim}

\begin{verbatim}
#> # A tibble: 670 x 8
#>     from    to  x_from  y_from    x_to    y_to from_count to_count
#>    <int> <int>   <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
#>  1     1     2 -0.1    -0.0892 -0.0167 -0.0892          0        0
#>  2    16    17 -0.0584 -0.0171  0.0249 -0.0171          0        0
#>  3     1    31 -0.1    -0.0892 -0.1     0.0550          0        0
#>  4    16    32 -0.0584 -0.0171 -0.0167  0.0550          0        0
#>  5     3    17  0.0665 -0.0892  0.0249 -0.0171          0        0
#>  6    17    18  0.0249 -0.0171  0.108  -0.0171          0        0
#>  7    17    33  0.0249 -0.0171  0.0665  0.0550          0        0
#>  8    31    46 -0.1     0.0550 -0.0584  0.127           0        0
#>  9    32    47 -0.0167  0.0550  0.0249  0.127           0        0
#> 10    32    33 -0.0167  0.0550  0.0665  0.0550          0        0
#> # i 660 more rows
\end{verbatim}

@@

\begin{verbatim}
ggplot() + 
  geom_trimesh(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) +
  coord_fixed()
\end{verbatim}

>>>>

#> # A tibble: 322 x 8

@@

#> # i 312 more rows

@@

trimesh <- gen_edges(tri_object = tr_object, a1 = hb_obj$a1, a2 = hb_obj$a2)
trimesh
\end{verbatim}

\begin{verbatim}
#> # A tibble: 653 x 8
#>     from    to  x_from  y_from    x_to    y_to from_count to_count
#>    <int> <int>   <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
#>  1     1     2 -0.1    -0.0892 -0.0167 -0.0892          0        0
#>  2    16    17 -0.0584 -0.0171  0.0249 -0.0171          0        0
#>  3    16    32 -0.0584 -0.0171 -0.0167  0.0550          0        0
#>  4     3    17  0.0665 -0.0892  0.0249 -0.0171          0        0
#>  5    17    18  0.0249 -0.0171  0.108  -0.0171          0        0
#>  6    17    33  0.0249 -0.0171  0.0665  0.0550          0        0
#>  7    31    46 -0.1     0.0550 -0.0584  0.127           0        0
#>  8    32    47 -0.0167  0.0550  0.0249  0.127           0        0
#>  9    32    33 -0.0167  0.0550  0.0665  0.0550          0        0
#> 10     4    18  0.150  -0.0892  0.108  -0.0171          0        0
#> # i 643 more rows
\end{verbatim}

@@

\begin{verbatim}
ggplot() + 
  geom_trimesh(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) 
\end{verbatim}
